---
title: "01-assignment_Voorhies"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(plotly)
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1: Hello World
```{r}
print("Hello World")
```

```{r}
## Load in the data
load("college.Rdata")
```

# Question 2: Summarizing College Data
## Question 2-1: Comparing earnings by Selective vs. Non Selective Schools

```{r}

## What's the average earnings for very selective schools?
sc%>%filter(adm_rate<.1)%>%summarize(mean_earnings=mean(md_earn_wne_p6,na.rm=TRUE))

## And for not very selective schools?
sc%>%filter(adm_rate>.3)%>%summarize(mean_earnings=mean(md_earn_wne_p6,na.rm=TRUE))

```

## Question 2-2: Are schools with high SAT scores smaller or larger?

```{r}


## What's the average SAT score?
sc%>%summarize(sat_avg=mean(sat_avg,na.rm=TRUE))

## What's the average number of undergraduates for schools with above average SAT scores?
sc%>%filter(sat_avg>1200.1)%>%summarize(mean_ugds=mean(ugds,na.rm=TRUE))

## What's the average number of undergraduates for schools with below average SAT scores?
sc%>%filter(sat_avg<1200.1)%>%summarize(mean_ugds=mean(ugds,na.rm=TRUE))

```
## Question 2-3: Debt and Cost of Attendance

```{r}

## Plot Cost and Debt
gg<-ggplot(data=sc, aes(x=costt4_a,
                         y=debt_mdn,
                         text=debt_mdn))

## Add Points
gg<-gg+geom_point(alpha=.5,size=.5)

## Add labels
gg<-gg+xlab("Cost")+ylab("Average Debt")

gg
```

This is not completely surprising, as this is positively skewed.  I would imagine the reason why debt is low for some of the colleges at $50k+ are due to more robust scholarships and student aid.

## Question 2-4: Plots for Cost and Debt by Control

```{r}

## Plot Cost by Control
gg<-ggplot(data=sc, aes(x=costt4_a,
                         y=control,
                         text=control))

## Add Points
gg<-gg+geom_point(alpha=1,size=1)

## Add labels
gg<-gg+xlab("Average Cost")+ylab("Control")

gg

## Plot Debt by Control
gg<-ggplot(data=sc, aes(x=debt_mdn,
                         y=control,
                         text=control))

## Add Points
gg<-gg+geom_point(alpha=1,size=1)

## Add labels
gg<-gg+xlab("Debt")+ylab("Control")

gg

```

